SIMD\slash SIMT-vectorized Sparse Chemical Kinetic Jacobian\slash Thermo-chemical Source Term Evaluation

### 2018-02-17 paper.tex
update error stats

\todo{rerun, especially H2 error}
\begin{table}[tbp]
\centering
\begin{tabular}{@{}l S S[table-format=1.3e1] S[table-format=1.3e1] S[table-format=1.3e1]@{}}
\toprule
Model                 & \multicolumn{1}{c}{Sample size}   & \multicolumn{1}{c}{$\bar{\mathcal{T}}$}  & \multicolumn{1}{c}{$E_{10^{20}}$}   & \multicolumn{1}{c}{$E_{10^{15}}$} \\
\midrule
\ce{H2}\slash \ce{CO} & \num{900900}                      & \num{6.431e+18}      & \num{8.083e-1}  & \num{1.907e-5} \\
GRI-Mech 3.0          & \num{450900}                      & \num{7.783e+19}      & \num{1.890e-7}  & \num{1.877e-7} \\
USC-Mech II           & \num{91800}                       & \num{2.830e+21}      & \num{5.567e-3}  & \num{1.704e-7} \\
\ce{iC5H11OH}         & \num{450900}                      & \num{2.733e+26}      & \num{1.136e-3}  & \num{2.764e-5} \\
\bottomrule
\end{tabular}
\caption{Summary of Jacobian matrix validation results.
Error statistics are the largest filtered relative error $E_\mathcal{C}$ for over all samples.
It is noted that the threshold described in~\cref{e:thresh} varies slightly between the \conp~and \conv~cases; the reported $\bar{\mathcal{T}}$ is the average of the two, however the appropriate value was used during calculations of the error statistics..
}
\label{T:error}
\end{table}

\Cref{T:error} presents the error statistics of \texttt{pyJac} over the tested PaSR thermo-chemical condition database.
For all tested cases, \todo{need srv2 nvidia tests to really confirm here} the maximum filtered error norm is less than unity.
The filtered error norm is largest for the \ce{H2}\slash\ce{CO} model with the more stringent tolerance ($\mathcal{C} = 10^{20}$).
We note that $\mathcal{T}$ for this model is smaller than the tolerance in this case, and hence we are comparing numbers smaller than $\mathcal{O}(1)$; relaxing the tolerance to $\mathcal{C} = 10^{15}$ significantly lowers the filtered error norm to $\mathcal{O}(10^{-5})$.
Similar error characteristics are seen for all models except GRI-Mech 3.0---in which the error norms for both tolerances are $\sim\mathcal{O}(10^{-7})$---that is a larger error norm for the more stringent tolerance that drops 2--4 orders of magnitude for the relaxed tolerance.

>>>>

\begin{table}[tbp]
\centering
\begin{tabular}{@{}l S S[table-format=1.3e1] S[table-format=1.3e1] S[table-format=1.3e1]@{}}
\toprule
Model                 & \multicolumn{1}{c}{Sample size}   & \multicolumn{1}{c}{$\bar{\mathcal{T}}$}  & \multicolumn{1}{c}{$E_{10^{20}}$}   & \multicolumn{1}{c}{$E_{10^{15}}$} \\
\midrule
\ce{H2}\slash \ce{CO} & \num{900900}                      & \num{6.431e+18}      & \num{8.084e-1}  & \num{1.907e-5} \\
GRI-Mech 3.0          & \num{450900}                      & \num{7.783e+19}      & \num{1.890e-7}  & \num{1.877e-7} \\
USC-Mech II           & \num{91800}                       & \num{2.830e+21}      & \num{1.540e-3}  & \num{1.704e-7} \\
\ce{iC5H11OH}         & \num{450900}                      & \num{2.733e+26}      & \num{1.363e-3}  & \num{2.764e-5} \\
\bottomrule
\end{tabular}
\caption{Summary of Jacobian matrix validation results.
Error statistics are the largest filtered relative error $E_\mathcal{C}$ for over all samples.
It is noted that the threshold described in~\cref{e:thresh} varies slightly between the \conp~and \conv~cases; the reported $\bar{\mathcal{T}}$ is the average of the two, however the appropriate value was used during calculations of the error statistics..
}
\label{T:error}
\end{table}

\Cref{T:error} presents the error statistics of \texttt{pyJac} over the tested PaSR thermo-chemical condition database.
For all tested cases, the maximum filtered error norm is less than unity.
The filtered error norm is largest for the \ce{H2}\slash\ce{CO} model with the more stringent tolerance ($\mathcal{C} = 10^{20}$).
We note that $\mathcal{T}$ for this model is smaller than the tolerance in this case, and hence we are comparing numbers smaller than $\mathcal{O}(1)$; relaxing the tolerance to $\mathcal{C} = 10^{15}$ significantly lowers the filtered error norm to $\mathcal{O}(10^{-5})$.
Similar error characteristics are seen for all models except GRI-Mech 3.0---in which the error norms for both tolerances are $\sim\mathcal{O}(10^{-7})$---that is a larger error norm for the more stringent tolerance that drops 2--4 orders of magnitude for the relaxed tolerance.
